\tool: Revisiting BadUSB with Type-C

### 2021-01-25 WOOT/Files/badusb.tex
Figure

We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector. As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to carry out their attacks precisely or confirm the effects after attacks.

@@

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. Based on this restriction, several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the BadUSB is only able to emulate a limited kind of devices like HID or disks, by no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge manually by the attacker. Moreover, with video capability combined with traditional BadUSB, our \tool achieved multiple new attack paradigm and are tested under various real-life scenarios.

@@

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
\end{itemize}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim. These constructed HID packet will be interpreted by the victim as valid keystrokes and mouse moves. Thus the attacker can executes arbitrary scripts on the victim's device. This is the function of the original BadUSB. Based on this, we made the following improvement.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}

>>>>

We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector. As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.

%\subsection{Motivation}
%\noindent\outline{Limitation of Rubber Ducky}\\
%\outline{Our functionality different mode listing?}\\
%\hongyi{The following mode is to be further decided}
%\outline{Automatic Scripting Mode}\\
%\outline{Remote Control Mode}\\
%\outline{OCR/QR Recognition Mode}\\

\subsection{Implementation}
%\noindent\hongyi{The following mode is to be further decided}\\
%\outline{DETAIL of each mode}\\
%\outline{Automatic Scripting Mode}\\
%\outline{Remote Control Mode}\\
%\outline{OCR/QR Recognition Mode}\\
As we introduced in Section~\ref{sec:related_work}, there are plenty of existing work~\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} focusing on BadUSB attack. 
Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to carry out their attacks precisely or confirm the effects after attacks.

@@

%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited. 
Based on the drawbacks introduced above, several defense mechanisms were proposed, like GoodUSB\cite{tian2015defending}. These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in. As the BadUSB is only able to emulate a limited kind of devices like HID or disks, by no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of bypassing this type of defense. Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge manually by the attacker. Moreover, with video capability combined with traditional BadUSB, our \tool achieved multiple new attack paradigm and are tested under various real-life scenarios.

@@

\subsubsection{Attack Model}
The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
\begin{itemize}
	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
\end{itemize}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.56\linewidth]{./Figs/attack_model.png}
	\caption{Attack Model}%\shuqing{Need to be more compact.}
	\label{fig:attack_model}
\end{figure}
\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim. These constructed HID packet will be interpreted by the victim as valid keystrokes and mouse moves. Thus the attacker can executes arbitrary scripts on the victim's device. This is the function of the original BadUSB. Based on this, we made the following improvement.

@@

This mode enable attacker to perform delicate operation that is beyond automation. Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}

### 2021-01-25 WOOT/Files/experiment.tex
[eperiment] photo of armory

\subsection{Case study}
\label{subsec:case_study}
\subsubsection{Background}

We conducted a case study with sharing power bank and QR code payment as technical background.

\textbf{Sharing Power Bank}. 
Sharing power bank provides users with short-term rental of power banks. 
The provider deploys power bank stations in the city, while the users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay the rent online.

As an example, Brick is such a power bank sharing service provider from Sweden. 
As Brick's website states, \textit{Brick prevents your electronics from running out of battery with power banks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.}. \yechang{citation needed}
\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

@@

Though it provides convenience to users, it also brings security issues. 
We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices to them. 
The attackers are able to modify their rented power banks, return it to a power bank station as normal.
Then the subsequent users will unknowingly connect to such malicious power banks, which endangers the financial security and data security of users.

\textbf{QR Code Payment}. 
QR code payment is a method of paying bills, typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. 
This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. 
By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. 
Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}

@@

In the real-world scenario, some payment service providers provide special rules for micropayment purchases. 
A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. 
For example, WeChat Pay~\cite{Wechat-pay} regards payments less than CNY \textyen 1000 as micropayments. 
Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further actions, which is often encouraged by the payment service provider.
The payment QR code is associated with the payer's account. 
If a victim's payment code is leaked to the attackers, they can use the that payment code to proceed payments. 
Furthermore, the attackers can use several micropayments to steal money from the victim's account, leaving the victim unconscious. 
\shuqing{Introduce something about QR code refreshing (fast).}
In summary, the payment QR code is highly sensitive on users' devices.

@@

Note that \tool only exposes a type-c cable (from USB Type-C hub).
It charges the attacker's device through this cable, which has no difference from ordinary power banks. 
Considering users' vigilance and high similarity between \tool and normal power banks, the attackers can put the modified power banks (e.g., \tool) in a power bank station.
Subsequent users may unconsciously connect their devices to \tool.
Like many outdoor mobile phone usage scenarios\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment with showing payment code. 
Then the attackers can extract and use the victim's payment code to make another payment unknown to the victim.
\shuqing{This paragraph is duplicate with some previous paragraphs. We can make the previous introduction abut attack scenario really brief, and mainly introduce it here.}

>>>>

\subsection{Case study}
\label{subsec:case_study}
\subsubsection{Background}
We first introduce the technical background of our case study, sharing power bank service and QR code payment.

\textbf{Sharing Power Bank}. 
Sharing power bank provides users with short-term rental of power banks. 
The company deploys power bank stations in the city and users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to the near station and pay the rent fee.

For an example, Brick is such a power bank sharing service provider from Sweden. It provides power bank rental service all over the Sweden and is planning on expanding their service around Europe. What's more, this service is even more popular in China, there are these stations being deployed in almost every market, store and even newsstand. This suggests that this service is becoming more and more common around the global, especially in China and Europe.
\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}

@@

Not only does sharing power bank provides convenience to users, but it also brings security issues. 
We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices. 
An attacker are able to modify his/her rented power banks and return it to a power bank station.
Then the next user will unknowingly connect to such a malicious power bank, which endangers his/her financial and data security.

\textbf{QR Code Payment}. 
QR code payment is a new type of payment method that are popular in China. Its most well known cases are WeChat Pay and Alipay. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card. This explains why it becoming widely used in China.
QR code payment is typically performed in the following steps:
\ding{182} The client presents payment QR code on mobile device to the merchant. 
The QR code is encoded with a globally unique ID to identify the client's account. 
\ding{183} The merchant scans the payment QR code and charges corresponding amount of money. 
By presenting this QR code, the client authorizes proceeding charge.
\ding{184} An transaction generated by this scan is sent to the payment service provider. 
Then the payment service provider requests the client to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

In the real-world scenario, some payment service providers provide special rules for micropayment purchases. 
A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. 
For example, WeChat Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as micropayments. 
Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without clients' permission which aims to provide convenience to both merchant and client.
If a victim's payment code is leaked to the attackers, they can use the that code to authorize multiple micropayments without permission. 
In order to prevent such cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the payment code, which is to refresh the QR code every minute. This is sufficient to stop attack like sneak shots, but unable to stop real-time attack like our \tool.
\shuqing{Introduce something about QR code refreshing (fast).}
In summary, the payment QR code is highly sensitive on users' devices and our following case study is about how to obtain this code using modified power bank, our \tool.

@@

Note that \tool only exposes a USB Type C cable (from USB Type-C hub), which looks just like a normal power bank. With the internal battery, \tool can provide sufficient power for both itself and the victim's device.
Considering normal users' vigilance and the high similarity between \tool and power banks, the attackers can easily put the modified power banks (e.g., \tool) in a power bank station.
Other users may unconsciously connect their devices to \tool.
As the QR code payment is fairly common\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment by showing their payment code. 
Then the attackers can extract and use the victim's payment code to make another payment unknown to the victim.
\shuqing{This paragraph is duplicate with some previous paragraphs. We can make the previous introduction abut attack scenario really brief, and mainly introduce it here.}

### 2021-01-25 WOOT/Files/introduction.tex

On the other side of the coin, the security of USB has caused serious problems.
The designers of USB protocol did not care much about security issues as they wanted to make a easy-to-use protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them from normal USB devices.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers and tablet computers, in order to validate the usability of \tool.
At last, we conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of privacy data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass most of the previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool. \shuqing{Notable results.}
\end{itemize}

>>>>

On the other side of the coin, the security of USB has caused serious problems.
The designers of USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.
These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
Such attacks can easily escape from traditional anti-virus software, since it is hard to distinguish them from normal USB devices.

Despite the advantageous features of BadUSB, there exist several limitations as follows.
(1) Attackers cannot conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
\tool extends BadUSB to support the features of USB Type-C.
Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
At last, we conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
%\shuqing{Case study, evaluation, notable results.}

We summarize our key contributions as follows:
\begin{itemize}
	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
	The combination of new support with conventional BadUSB makes attacks more precise and effective.
	\item Our approach can bypass most of the previous countermeasures of BadUSB.
	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool. \shuqing{Notable results.} \fengwei{Add countermeasures, in particular the isolation design.}
\end{itemize}
